Implementation of Concurrent Hash Tables in Java

### 2022-04-29 paper.tex
Section For Fine-Grain Table

>>>>

\subsection{Fine-Grain Locking Hashtable}

\begin{lstlisting}[language={Java},caption=Source code for the fine-grain put() method.,captionpos=b,breaklines=true,frame=single]
public boolean put(int item) {
    // If capacity if full, do not add
    if (capacity >= ARR_SIZE)
        return false;

    // Quadratically probe for empty indices
    int i = 0;
    int new_key = (key + (i * i)) % ARR_SIZE;
    while (true) {
        if (table[new_key] == null) {
            locks[new_key].lock();
            // Make sure still null
            if (table[new_key] == null) {
                table[new_key] = item;
                cleans[new_key] = false;
                locks[new_key].unlock();
                break;
            }
            locks[new_key].unlock();
        }

        i++;
        new_key = (new_key + (i * i)) % ARR_SIZE;
    }

\begin{lstlisting}[language={Java},caption=Source code for the fine-grain search() method.,captionpos=b,breaklines=true,frame=single]
public boolean search(int item) {
    int key = hash(item);
    int i = 0;
    int new_key = (key + (i * i)) % ARR_SIZE;
    // Quadratically probe for the item
    // Dirty indices are considered to be a collision, the item may of been probed
    // farther down
    while (!cleans[new_key]) {
        if (item == table[new_key]) {
            return true;
        }
        i++;
        new_key = (new_key + (i * i)) % ARR_SIZE;
        if (i >= ARR_SIZE)
            break;
    }

\begin{lstlisting}[language={Java},caption=Source code for the fine-grain remove() method.,captionpos=b,breaklines=true,frame=single]
public boolean remove(int item) {
    int key = hash(item);
    int i = 0;
    int new_key = (key + (i * i)) % ARR_SIZE;

    // Quadratically probe for the item
    // Dirty indices are considered to be a collision, the item may of been probed
    // farther down
    while (!cleans[new_key]) {
        if (item == table[new_key]) {
            locks[new_key].lock();
            table[new_key] = null;
            locks[new_key].unlock();
            break;
        }
        i++;
        new_key = (new_key + (i * i)) % ARR_SIZE;
    }
